---
title: "Getting Player Max's"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{get-max}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This Guide will explain how to access an entire team 1 rep max and 1 rep power max.



# Set up API Token

Below is the code to set up your API Token. Please reference the [Get Started Guide](getting-started.html).
```{r setup, eval = FALSE}
# Load the eliteformR package
library(eliteformR)

API_key <- "YOUR-API-KEY-HERE"
URL <- "https://your_team_url_eliteform.com"

token <- EF_CreateAPIToken(URL, API_key)

# Download Team List
team_list_df <- EF_GetTeamsList(token)

# Update the Token with the Selected Team ID
# TeamId should be as.numeric()
token <- EF_UpdateTokenTeam(token, team_list_df$TeamId[1])
# or 
# token <- EF_UpdateTokenTeam(token, 111)
```

# Get Team's Current 1 Rep Max

To gather your Team's current 1 rep maxes, you will require just the token. 

```{r, eval = FALSE}
Team1RepMax_df <- EF_Get1RMs(token)

Team1RepMax_df

#           Date AthleteId     LastName FirstName    Exercise Result
# 1     6/8/2023      4342       Player         1       SQUAT    450
# 2     5/8/2023      4342       Player         1 POWER CLEAN    302
# 3    7/12/2023      4342       Player         1 BENCH PRESS    356
# 4    5/28/2024      4343       Player         2       SQUAT    100
# 5    5/28/2024      4343       Player         2 POWER CLEAN    100
# 6    5/28/2024      4343       Player         2 BENCH PRESS    100
# 7    7/27/2025      4344       Player         3       SQUAT    360
# 8    5/27/2025      4344       Player         3 POWER CLEAN    314
# 9    7/29/2025      4344       Player         3 BENCH PRESS    320

```

# Get Team's Current Power 1 Rep  Max

To gather your Team's current power 1 rep maxes, you will require just the token. 


```{r, eval = FALSE}
Power.Team1RepMax_df <- EF_GetPower1RMs(token)

Power.Team1RepMax_df

#           Date AthleteId     LastName FirstName    Exercise Result
# 1     6/8/2023      4342       Player         1       SQUAT    450
# 2     5/8/2023      4342       Player         1 POWER CLEAN    302
# 3    7/12/2023      4342       Player         1 BENCH PRESS    356
# 4    5/28/2024      4343       Player         2       SQUAT    100
# 5    5/28/2024      4343       Player         2 POWER CLEAN    100
# 6    5/28/2024      4343       Player         2 BENCH PRESS    100
# 7    7/27/2025      4344       Player         3       SQUAT    360
# 8    5/27/2025      4344       Player         3 POWER CLEAN    314
# 9    7/29/2025      4344       Player         3 BENCH PRESS    320

```

































